---
title: "GreatPlainsBCGCalc-NEWS"
author: "Ben.Block@tetratech.com"
date: "`r Sys.time()`"
output: github_document
  #md_document:
   # variant: markdown_github
---

<!-- NEWS.md is generated from NEWS.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "NEWS-"
)
```

```{r, echo = FALSE}
cat(paste0("Last Update: ",Sys.time()))
```

# GreatPlainsBCGCalc 0.0.3.9001 (2024-06-06)

* refactor: Update map_meta file for missing column name
   + Gets rid of message to console; New names: ...1

# GreatPlainsBCGCalc 0.0.3.9000 (2024-05-30)

* Add trim_ws parameter as TRUE to taxa_translate routine in Shiny app
* Add metric calculation code for quant v. qual samples (IA and MO)

# GreatPlainsBCGCalc 0.0.2.9000 (2024-05-14)

* Bug models calculating correctly

# GreatPlainsBCGCalc 0.0.1.9000 (2024-05-07)

* Updated with Great Plains specific information
* Fish models calculating correctly
   
# GreatPlainsBCGCalc 0.0.0.9000 (2024-05-06)

* Created GitHub repository
* docs: Add base package files from NM_BCGCalc (Blocktt)
   + DESCRIPTION
   + NEWS
   + README
   + app function

